Colonies - Compute Continuums across Platforms

### 2023-04-08 paper_2023/paper.tex
wip

\subsubsection{Generators}
Another features of the Colonies framework are so-called generators. Generators are workflow templates that are triggered automatically when specific conditions are met. Generators can for example be used accumulate input data in bulks to improve performance or parallelism. This is achieved by sending a special \emph{pack request} to a Colonies server, targeting a certain generator. Generators facilities integration with third-party systems as it allows for stateless implementation where interactions with Colonies can occur using a fire-and-forget style. Colonies guarantees that all pack request submitted to a generator is evenutally processed, even if a Coloniers server is restarted or fails.

Without generators, third-party software would have to use an alternative method such as a message broker or a database to enqueue input data and periodically empty the queues to generate workflows themselves. This adds complexity to the integration process and may requires additional infrastructure components. Generators are a powerful feature of the Colonies framework that can help simplify integration and implement robust data processing pipelines.

Generators can be implemented using a similar method to how Cron workflow are implemented. The elected leader Colonies server is responsible for scanning a special generator table database to decide if a workflow should be triggered. This approach ensures that there is a single point of control for generating workflows and prevents generation of duplicate workflows.

If the leader server crashes, a new leader Colonies server is automatically elected, and it takes over the responsibility for triggering the generators. This ensures that the generation of workflows is not impacted by server failures, and the system can continue to operate smoothly even in case of failures. It can be worth to point out that since the pack request only adds information to the database and does not manipulate any states, it can be processed by any Colonies server without synchronization precautious. This means that any server in the cluster can handle incoming pack requests, which increases the scalability and fault-tolerance of the system.

>>>>

\subsubsection{Generators}
Another features of the Colonies framework are so-called generators. Generators are workflow templates that are triggered automatically when specific conditions are met. Generators can be used accumulate input data in bulks to improve performance or parallelism. For example, an external service downloads satellite images and a workflow should automatically be triggered when 10 images are collected. This is achieved by sending a special \emph{pack request} containing input data to a Colonies server, targeting a certain generator.

Generators facilities integration with third-party systems as it allows for stateless implementation where interactions with Colonies can be done in a fire-and-forget style. Colonies guarantees that all pack requests submitted to a generator is processed correctly, even if a Colonies server is restarted or fails. Without generators, third-party software would have to use an alternative method such as a message broker or a database to enqueue input data and periodically empty the queues to generate workflows themselves. This adds complexity to the integration process and may requires additional infrastructure components. Generators are a powerful feature of the Colonies framework that can help simplify integration and implement robust data processing pipelines.

Generators can be implemented using a similar method to how Cron workflow are implemented. The elected leader Colonies server is responsible for scanning a special generator table to decide if a workflow should be triggered. This approach ensures that there is a single point of control for generating workflows and prevents generation of duplicate workflows. If the leader server crashes, a new leader Colonies server is automatically elected, and it takes over the responsibility for triggering the generators. This ensures that the generation of workflows is not impacted by server failures, and the system can continue to operate smoothly even in case of failures. It can be worth to point out that since the pack request only adds information to the generator table and does not manipulate any states, it can be processed by any Colonies server without synchronization precautious. This means that any Colonies server in the cluster can handle incoming pack requests, which increases the scalability and fault-tolerance of the system as a whole.
